\Title

### 2021-01-27 manuscript/manuscript.tex

\begin{abstract}
    My abstract
    \\[0.5cm]
    \textbf{Keywords:}
    My keywords
\end{abstract}

@@

We are indebted to the developers and maintainers of the open-source software
without which this work would not have been possible.
Contains British Geological Survey materials © UKRI.

>>>>

\noindent
\textbf{Keywords:}
Gravity anomalies and Earth structure;
Magnetic anomalies: modelling and interpretation;
Geopotential theory;
Inverse theory;
Statistical methods;
Australia;

\begin{abstract}
  The equivalent source technique is a powerful and widely used method for
  processing gravity and magnetic data.  Nevertheless, its major
  drawback is the large computational cost in terms of processing time and
  computer memory.
  We present two techniques for reducing the computational cost of equivalent
  source processing: block-averaging source locations and the
  gradient-boosted equivalent source algorithm.
  By using block-averaging, we reduce the number of source coefficients that
  must be estimated while retaining the minimum desired resolution in the final
  processed data.
  With the gradient boosting method, we estimate the layer coefficients in
  small batches along overlapping windows, allowing us to reduce the computer
  memory requirements arbitrarily to conform to the constraints of the
  available hardware.
  We show that the combination of block-averaging and gradient-boosted
  equivalent sources are capable of producing accurate interpolations through
  tests against synthetic data.
  Moreover, we demonstrate the feasibility of our method by gridding a gravity
  dataset covering Australia with over 1.7 million observations using a modest
  personal computer.
\end{abstract}

@@

We are indebted to the developers and maintainers of the open-source software
without which this work would not have been possible.
S.R. Soler is supported by a scholarship from CONICET, Argentina.
Contains British Geological Survey materials © UKRI.

S.R. Soler and L. Uieda jointly developed the initial idea, analysed the
results, and wrote the paper. S.R. Soler produced all results and developed the
software implementation with minor revisions by L. Uieda.
